Databrary: A digital data library for sharing research video

### 2015-01-29 jcdl-15/paper.tex
Minor editing intro, reflow

Video and audio recordings serve as a primary data source in psychology, linguistics, education, anthropology, and numerous other fields, especially the study of human and animal development.
Unfortunately, researchers who collect video rarely share recordings with others, due largely to perceived requirements associated with privacy restrictions.
The goal of the Databrary project is to increase the repurposing and reuse of recordings, especially video, by creating tools that allow video to be documented, organized, and shared among researchers.
We have created a web-based data library to accommodate the storage and organization of video data, capture contextual information necessary for reuse, and standardize across datasets without placing undue burden on data contributors.
In this paper, we discuss the design and technical challenges of the system and describe some findings and structural solutions to these challenges.

@@

Research data repositories require a balance between generality and specificity.
Archives that permit the unstructured storage of arbitrary files lie at one extreme;
those that present a rigorously structured schema and required contribution formats lie at the other.
The flexibility of general-purpose repositories make them especially well-suited to the archival of entire datasets, but these systems do not facilitate search, understanding, or re-use without extensive, usually labor-intensive, curation \cite{Peer_2012}.
Targeted repositories, on the other hand, generate large-scale, homogeneous data sources that facilitate meta- and re-analysis, but serve only specific domains. 
We have attempted to strike a balance between these extremes by making video and audio recordings the unifying focus of Databrary. This allows additional structured and unstructured resources to be built around and discovered through this functional core.

@@

Research using recordings typically proceeds with the addition of temporally-positioned annotations, either by direct observation or with the aid of simple visualization or analysis tools.
Specialized desktop software tools --- both commercial (e.g., Noldus Observer, Mangold Interact, and Studiocode) and academic (e.g. Transana, Elan, CLAN, and Datavyu) --- enable researchers to annotate events, measurements, utterances, or behaviors at any temporal scale, from individual samples/frames to the entire session.
Most of these tools currently focus on a single recording, and despite the plethora of tools and features, there is little interoperability.
Moreover, with rare exceptions \cite{MacWhinney2001} there are few standards for annotations themselves, even across studies performed by the same researcher. %Adolph, personal communication?

>>>>

Video and audio recordings serve as a primary data source in psychology, linguistics, education, anthropology, and numerous other fields, and especially in the study of human development.
Unfortunately, researchers who collect recordings rarely share with others, due largely to perceived requirements associated with privacy restrictions.
The goal of the Databrary project is build tools and policies that simplify repurposing and reuse of recordings.
We have created a web-based data library to accommodate the storage and organization of video data, capture contextual information necessary for reuse, and standardize across datasets without placing undue burden on data contributors.
In this paper, we discuss the design and technical challenges of the system and describe some findings and structural solutions to these challenges.

@@

Research data repositories require a balance between generality and specificity.
Archives that permit the unstructured storage of arbitrary files lie at one extreme; those that present a rigorously structured schema and required contribution formats lie at the other.
The flexibility of general-purpose repositories make them especially well-suited to the archival of entire datasets, but these systems do not facilitate search, understanding, or re-use without extensive, usually labor-intensive, curation \cite{Peer_2012}.
Targeted repositories, on the other hand, generate large-scale, homogeneous data sources that facilitate meta- and re-analysis, but are limited to specific research questions, losing the full richness, context, and innovation of the source materials and field.
We have attempted to strike a balance between these extremes by making video and audio recordings the unifying focus of Databrary.
This allows additional structured and unstructured resources to be built around and discovered through this functional core.

@@

Research using recordings typically proceeds with the addition of temporally-positioned annotations, either by direct observation or with the aid of simple visualization or analysis tools.
Specialized desktop software tools---both commercial (e.g., Noldus Observer, Mangold Interact, and Studiocode) and academic (e.g., Transana, Elan, CLAN, and Datavyu)---enable researchers to annotate events, measurements, utterances, or behaviors at any temporal scale, from individual samples/frames to the entire session.
Most of these tools currently focus on a single recording, and despite the plethora of tools and features, there is little interoperability.
Moreover, with rare exceptions \cite{MacWhinney2001} there are few standards for annotations themselves, even across studies performed by the same researcher. %Adolph, personal communication?
